Demes: a specification for interchanging complex demography

### 2021-06-19 paper.tex
Added scope of spec section

\subsection*{Design rationale}

This is an unstructured list of things we should mention in terms
of why certain decisions were made

\begin{itemize}
    \item Recent developments in software engineering have favoured
    static, declarative configuration formats. It feels like a good idea to
    have a Turing complete configuration format, but it turns out not to be.

    \item Drawing parameters from distributions. Why we are static.
    % https://github.com/popsim-consortium/demes-paper/issues/3

    \item Why we've avoided turning this into a model of everything, allowing
    for the specification of genome properties like recombination rates,
    etc.

>>>>

\subsection*{Scope of the specification}
\jkcomment{This section is very rough.}

% https://github.com/popsim-consortium/demes-paper/issues/3

The Demes specification is by design simple and static---we wish to
unambiguously describe a demographic model with fully specified
and fixed parameters. This simplicity means that we cannot directly
specify distributions or estimated confidence intervals
for those parameters. While it is not difficult to imagine extending
the specification in ways that would allows us to do this, it would
greatly increase the complexity of parsers and would likely be of
little practical use in any case. This is because the parameters of
demographic models are typically tightly coupled, and cases in which
distributions for different parameters can be simply described are rare.
In this situation, the simplest way to describe estimated
distribution is simply to list a large number samples from
the posterior. While writing out a large number of Demes models in
YAML format may seem inefficient, it can in fact be a compact
way to describe these distributions.
\jkcomment{TODO: add in a quick example here where we take an IM model
and simulate a posterior distribution under some reasonable model. Report
how much space it takes to represent a large number of samples from this
distribution}

Similarly, one might be interested in running simulations in which
the demographic model parameters are drawn from a distribution, e.g.,
in ABC inference~\citep{beaumont2002approximate}. Allowing for
the many distributions of interest would greatly increase the complexity
parsers, with a relatively limited benefit. It would be far simpler
and more powerful to write some code to sample directly from the
distributions of interest, using, for example the Demes Python
API.
\jkcomment{This is garbled, but we get the point? You're probably never
going to be doing ABC from a completely general Demes model as input.
There will be some basic model that you have in mind, that you're generating
distributions of parameters around. So, what's the point in writing
general machinery to do this sampling, when you could write it yourself in
10 lines of Python?}

\begin{itemize}
    \item Why we've avoided turning this into a model of everything, allowing
    for the specification of genome properties like recombination rates,
    etc.
